\documentclass[12pt, a4paper]{article}

% Standard packages for economics papers
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{setspace}
\onehalfspacing % Common for readability; use \doublespacing if submitting for review
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

% Papers to make the tables render correctly
\usepackage[utf8]{inputenc}
\usepackage{booktabs}  % Creates beautiful top/mid/bottom rules instead of ugly grids
\usepackage{multirow}  % Allows the p0 values to span across the T rows seamlessly

% BibLaTeX setup for Zotero Better BibLaTeX
\usepackage[style=authoryear, backend=biber, natbib=true, maxcitenames=2]{biblatex}
\addbibresource{Monte Carlo Simulations.bib}

% Title and Author Information
\title{BVAR vs. Information Criteria: A Monte Carlo Simulation Study}
\author{
    Ak\i n Ayd\i n\thanks{Ludwig-Maximilian University of Munich, \href{mailto:akin.aydin@campus.lmu.de}{akin.aydin@campus.lmu.de}} \and
    Ferdinand Loser\thanks{Ludwig-Maximilian University of Munich, \href{mailto:ferdinand.loser@campus.lmu.de}{ferdinand.loser@campus.lmu.de}}
}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
\noindent
This is the abstract for your paper. Briefly state the purpose of the research, the principal results, and major conclusions. The abstract should be self-contained and citation-free.
\vspace{1em}\\
\noindent\textbf{Keywords:} Keyword 1, Keyword 2, Keyword 3 \\
\noindent\textbf{JEL Codes:} C15, C32 % Update with relevant JEL classification codes
\end{abstract}

\newpage

\section{Introduction}
\label{sec:introduction}


\section{Methodology}
\label{sec:methodology}

Describe your structural VAR (SVAR) models and the Monte Carlo Data Generating Processes (DGPs) here.

\subsection{Data Generating Process}
Explain the true DGP based on Johansen and Juselius (1990), Ramey (2011), or Kilian and Murphy (2014).

\section{Simulation Results}
\label{sec:results}

Present the results of your Monte Carlo simulations. 

\input{Tables/Table_Paper1_BVARs.tex}
\input{Tables/Table_Paper2_BMA.tex}

\section{Conclusion}
\label{sec:conclusion}

Summarize the main findings and implications for applied macroeconomic research.

\newpage
% Print the bibliography
\printbibliography

\end{document}
