\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{setspace}

\onehalfspacing

\title{Research Proposal: Reliability of Information Criteria in Determining VAR Lag-Orders for Macroeconomic IRF Analysis}
\author{Akin Aydin and Ferdinand Loser}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Briefly summarize the motivation, methodology, and expected outcomes of your Monte Carlo simulation project testing VAR lag-order information criteria (AIC, SIC, HQC) and their effect on Impulse Response Functions (IRFs) or Persistence Profiles.
\end{abstract}

\section{Introduction}
Introduce the importance of Vector Autoregression (VAR) and VECM models in macroeconomics (e.g., Johansen-Juselius 1990, Ramey 2011). Discuss the challenge of selecting the correct lag order and how incorrect choices impact structural analysis and policy implications.

\section{Literature Review}
Review existing literature on lag selection criteria. Discuss the theoretical trade-offs between the Akaike Information Criterion (AIC), Schwarz/Bayesian Information Criterion (SIC/BIC), and Hannan-Quinn Criterion (HQC) in small versus large samples. 

\section{Methodology}

\subsection{Data Generating Processes (DGPs)}
Describe how you will construct your DGPs based on empirical macroeconomic datasets (e.g., extracting parameters by force-fitting models on the Johansen-Juselius dataset and Ramey 2011 dataset).

\subsection{Monte Carlo Simulation Design}
Explain the core simulation loop:
\begin{itemize}
    \item Drawing synthetic Gaussian innovations based on empirical covariance matrices.
    \item Generating synthetic time series of length $T$.
    \item Fitting restricted VAR/VECM models for test lags $1$ to $p_{max}$.
    \item Recording the lag selected by AIC, SIC, and HQC.
    \item Calculating the Mean Squared Error (MSE) of the resulting IRFs/Persistence Profiles compared to the true profile.
\end{itemize}

\section{Expected Results}
Discuss your hypotheses. For example, do you expect AIC to over-parameterize the model? Do you expect SIC to be more accurate in large samples but underfit in small samples ($T=80$)? How will these selection errors specifically distort the estimated Impulse Response Functions?

\section{Timeline}
Provide a brief schedule for completing the DGP extractions, Monte Carlo simulation coding in R, and the final write-up.

\newpage

% To use this, create a references.bib file in the same directory.
% Add your citations there (e.g., Ivanov & Kilian 2005, Ramey 2011).
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}